Process Genotypes For Ancestry Analysis

### 2019-09-19 code/Ancestry_PCA.Rmd
Chunk1v3

#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
for i in {1..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done

#Merge All Plink Chr Files 
for i in {2..22}
do
  echo 1000Genomes_chr$i >> Merge.list
done

plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

rm 1000Genomes_chr*
rm *.list
rm *.panel

@@

@@

#Reformat SNP List for plink filter.txt
 awk '{ print $1"\t"$4"\t"$4"\t"$2 }' INDV_1000G_Pops.bim > LDREF_SNPs.txt

@@

>>>>

##Pull The LDREF Panel SNPS
#Pull LDREF Data
wget https://data.broadinstitute.org/alkesgroup/FUSION/LDREF.tar.bz2
tar xjvf LDREF.tar.bz2

#Merge  LDREF Data
for i in {2..22} 
do 
    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
done 
plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef

#Write SNP List for LDREF Data
plink --threads $CORES --bfile TotalLDRef --write-snplist --out LDREF_SNPs

#Reformat SNP List for plink filter.txt
 awk '{ print $1"\t"$4"\t"$4"\t"$2 }' TotalLDRef.bim > LDREF_SNPs.txt

rm -r LDREF/

#Pull 1000G Data, convert to plink, Filt for INDV and SNPs
for i in {1..22}
#for i in {20..22}
do
	wget ftp://ftp-trace.ncbi.nih.gov/1000genomes/ftp/phase1/analysis_results/integrated_call_sets/ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz

    plink --vcf ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz --snps-only --extract LDREF_SNPs.txt --keep 1000G_IDV.list --threads $CORES --make-bed --out 1000Genomes_chr$i
  rm ALL.chr$i\.integrated_phase1_v3.20101123.snps_indels_svs.genotypes.vcf.gz
done

#Merge All Plink Chr Files 
for i in {2..22}
#for i in {21..22}
do
  echo 1000Genomes_chr$i >> Merge.list
done

#_#plink --bfile 1000Genomes_chr1 --merge-list Merge.list --make-bed --out 1000Genomes_Merged
plink --bfile 1000Genomes_chr20 --merge-list Merge.list --make-bed --out 1000Genomes_Merged

#rm 1000Genomes_chr*
rm *.list
rm *.panel
rm LDREF.tar.bz2
rm MergedChrs.txt

@@

#Merge  LDREF Data
for i in {2..22} 
do 
    echo LDREF/1000G.EUR.$i>> MergedChrs.txt
done 
plink --bfile LDREF/1000G.EUR.1 --threads $CORES --merge-list MergedChrs.txt --make-bed --allow-no-sex --out TotalLDRef

@@

#Reformat SNP List for plink filter.txt
awk '{ print $1"\t"$4"\t"$4"\t"$2 }' 1000Genomes_Merged.bim > LDREF_SNPs.txt

@@

## ReName the MSBB SNPS so the can be combined
```{python ReNamer}
import sys
import os
import re

###This Script reannotates bim file name from a snp list
#Usage:
# python BimAnotator.py TotalLDRef.bim LDREF_FiltSNPs.bim

InFile = TotalLDRef.bim       #sys.argv[1];
#Gene_Annots/hg19/Merged_hg19_Filt_ENGS.bed
InFileb = LDREF_FiltSNPs.bim  #sys.argv[2];

RS_IDs = {}
RS_Pos = {}

F1 = open(InFile)
for line in F1:
	LINE = line.rstrip('\r\n')
	lst = LINE.split('\t')

	RS_IDs[ ''.join([lst[0], '_', lst[3]]) ] = lst[1]
	RS_Pos[ ''.join([lst[0], '_', lst[3]]) ] = lst[2]
F1.close()

#Open Output
OUT = open( ''.join([ InFileb.replace(".bim", ""), 'Renamed.bim']), 'w' )

F1 = open(InFileb)
for line in F1:
	LINE = line.rstrip('\r\n')
	lst = LINE.split('\t')

	Name = RS_IDs[ ''.join([ lst[0], "_", lst[3] ])]
	Post = RS_Pos[ ''.join([ lst[0], "_", lst[3] ])]

	Entry = '\t'.join([ lst[0], Name, Post, lst[3], lst[4], lst[5] ])
	print >>OUT, Entry

F1.close()
```
